Evaluating Model Performances

### 2019-08-29 Scripts/evaluating_model_performances_rf.Rmd
changed formatting of error bars

```{r}
ggplot(all_rfperfs_mcc[all_rfperfs_mcc$CL=="GM12878",], aes(x=Resolution, y=MCC, color=Predictor, fill=Predictor, group=Predictor)) +
     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
     geom_bar(stat="identity", position = position_dodge()) +
     facet_grid(. ~ Resampling)+
     theme_minimal() +
     theme_bw()+
     xlab("Resolution") + ylab("MCC") + ylim(-.1,.5) +
     scale_fill_discrete(name="Predictor Type")+
     guides(color=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     strip.text.x = element_text(size = 15),
     strip.text.y = element_text(size = 15),
     panel.spacing = unit(2, "lines"),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20),
     legend.position="bottom")

@@

```{r}
ggplot(all_rfperfs_mcc[all_rfperfs_mcc$CL=="K562",], aes(x=Resolution, y=MCC, color=Predictor, fill=Predictor, group=Predictor)) +
     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
     geom_bar(stat="identity", position = position_dodge()) +
     facet_grid(. ~ Resampling)+
     theme_minimal() +
     theme_bw()+
     xlab("Resolution") + ylab("MCC") + #ylim(-.1,.5) +
     scale_fill_discrete(name="Predictor Type")+
     guides(color=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     strip.text.x = element_text(size = 15),
     strip.text.y = element_text(size = 15),
     panel.spacing = unit(2, "lines"),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20),
     legend.position="bottom")
```

>>>>

```{r}
ggplot(all_rfperfs_mcc[all_rfperfs_mcc$CL=="GM12878",], aes(x=Resolution, y=MCC, color=Predictor, fill=Predictor, group=Predictor)) +
     geom_bar(stat="identity", position = position_dodge()) +
     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.75,
                 position=position_dodge(.9), alpha=0.75, color="black", size=1) +
     facet_grid(. ~ Resampling)+
     theme_minimal() +
     theme_bw()+
     xlab("Resolution") + ylab("MCC") + ylim(-.1,.5) +
     scale_fill_discrete(name="Predictor Type")+
     guides(color=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     strip.text.x = element_text(size = 15),
     strip.text.y = element_text(size = 15),
     panel.spacing = unit(2, "lines"),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20),
     legend.position="bottom")

@@

```{r}
ggplot(all_rfperfs_mcc[all_rfperfs_mcc$CL=="K562",], aes(x=Resolution, y=MCC, color=Predictor, fill=Predictor, group=Predictor)) +
     geom_bar(stat="identity", position = position_dodge()) +
     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.75,
                 position=position_dodge(.9), alpha=0.75, color="black", size=1) +
     facet_grid(. ~ Resampling)+
     theme_minimal() +
     theme_bw()+
     xlab("Resolution") + ylab("MCC") + #ylim(-.1,.5) +
     scale_fill_discrete(name="Predictor Type")+
     guides(color=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     strip.text.x = element_text(size = 15),
     strip.text.y = element_text(size = 15),
     panel.spacing = unit(2, "lines"),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20),
     legend.position="bottom")
```
